---
title: "Modified EB Boot"
author: "Logan Harris"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ncvreg)
library(statmod)
library(ggplot2)

eb_boot <- function(beta, p = 60, b = 2, n = 100, niter = 100) {
  
  ## set.seed(12345)
  dat <- genDataABN(beta = beta, p = p, a = length(beta), b = b, n = n)
  
  tbeta <- dat$beta
  X <- dat$X
  y <- dat$y
  
  cv_res <- cv.ncvreg(X, y, penalty = "lasso")
  sigma2 <- cv_res$cve[cv_res$lambda == cv_res$lambda.min]
  lam <- cv_res$lambda.min
  
  lowers <- matrix(nrow = niter, ncol = length(tbeta))
  uppers <- matrix(nrow = niter, ncol = length(tbeta))
  for (i in 1:niter) {
    
    idx_new <- sample(1:length(y), replace = TRUE)
    ynew <- y[idx_new]
    xnew <- X[idx_new,,drop=FALSE]
    
    fit <- ncvreg(xnew, ynew, penalty = "lasso", lambda.min = lam*.1)
    print(fit$lambda)
    print(lam)
    coefs <- coef(fit, lambda = lam)
    
    t2i_scale <- lam^2
    
    ## Beta specific
    for (j in 1:length(tbeta)) {
      
      r <- ynew - (coefs[1] + xnew[,-j] %*% coefs[-1][-j])
      beta <- coefs[-1][j]
      tau2i_mu <- sqrt((sigma2*lam^2) / beta^2)
      tau2 <- 1 / rinvgauss(1, tau2i_mu, t2i_scale)
      
      A <- (t(xnew[,j, drop=FALSE]) %*% xnew[,j,drop=FALSE]) + (1/tau2)
      mu <- solve(A)*(t(xnew[,j,drop=FALSE]) %*% r)
      ci <- qnorm(c(.1, .9), mu, sqrt(sigma2*solve(A)))
      lowers[i,j] <- ci[1]; uppers[i,j] <- ci[2]
      
    }
    
  }
  
  return(list("lower" = lowers, "upper" = uppers, "truth" = tbeta))
  
}

plot_boot <- function(eb_boot) {
  
  lowers <- apply(eb_boot[["lower"]], 2, mean)
  uppers <- apply(eb_boot[["upper"]], 2, mean)
  plot_res <- data.frame(truth = eb_boot[["truth"]], grp = names(eb_boot[["truth"]]), lower = lowers, upper = uppers)
  
  plot_res %>%
    ggplot() +
    geom_point(aes(x = truth, y = grp)) +
    geom_errorbar(aes(xmin = lower, xmax = upper, y = grp)) +
    theme_bw()

}

eb_boot_sim <- function(beta, p = 60, b = 2, n = 100, niter = 100, nboot = 100) {

  overall_cov <- numeric(nboot)
  indiv_cov <- matrix(nrow = nboot, ncol = p)
  
  pb <- txtProgressBar(1, nboot, style=3)
  
  ## p, beta, n
  for (iter in 1:nboot) {
  
    res <- eb_boot(beta = beta, p = p, b = b, n = n, niter = niter)
    
    lower_int <- apply(res[["lower"]], 2, mean)
    upper_int <- apply(res[["upper"]], 2, mean)
    tbeta <- res[["truth"]]
    
    indiv_cov[iter,] <- tbeta >= lower_int & tbeta <= upper_int
    overall_cov[iter] <- mean(indiv_cov[iter,])
    
    setTxtProgressBar(pb, iter)
  
  }
  
  return(list("overall_cov" = overall_cov, "indiv_cov" = indiv_cov, "truth" = tbeta))

}
```

Interval widths are set to be 80%.

# One Covariate

## Beta = 0

### Single Example

```{r}
beta0 <- eb_boot(beta = 0, p = 1, b = 0, n = 30, niter = 100)
c(mean(beta0$lower), mean(beta0$upper))
```

### Coverage

```{r, eval=FALSE}
set.seed(1234)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, niter = 100, nboot = 100); save(res, file = "beta0_cov.rds")
mean(res$overall_cov)
```

```{r, echo=FALSE}
load("/Users/loganharris/github/lasso-boot/web/data/beta0_cov.rds")
mean(res$overall_cov)
```


## Beta = 3

```{r}
beta0 <- eb_boot(beta = 3, p = 1, b = 0, n = 30, niter = 100)
c(mean(beta0$lower), mean(beta0$upper))
```

```{r, eval = FALSE}
set.seed(1234)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, niter = 100, nboot = 100); save(res, file = "beta3_cov.rds")
mean(res$overall_cov)
```

```{r, echo=FALSE}
load("/Users/loganharris/github/lasso-boot/web/data/beta3_cov.rds")
mean(res$overall_cov)
```

# Many Covariates

## Not High Dimensional

### Single Example

```{r}
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5))
plot_boot(tmp)
```


### Coverage

```{r, eval = FALSE}
set.seed(123)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5))
save(res, file = "many.rds")
```

```{r, echo=FALSE}
load("/Users/loganharris/github/lasso-boot/web/data/many.rds")
```

#### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov)
```

#### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage)
```

## n = p

Here, I simply increase the number of true zeros. What I was interested in seeing was: 1) does the increase in sparsity effect the coverage of the non-zero coefficients, 2) Does it impact the marginal coverage rate?

### Single Example

```{r}
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), p = 100)
plot_boot(tmp)
```


### Coverage

```{r, eval = FALSE}
set.seed(123)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), p = 100)
save(res, file = "nep.rds")
```

```{r, echo=FALSE}
load("/Users/loganharris/github/lasso-boot/web/data/nep.rds")
```

#### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov)
```

#### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage)
```

## Increating betas, Not High Dimensional


### Single Example

```{r}
tmp <- eb_boot(beta = c(0.25, 0.5, 0.75, 1, 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5))
plot_boot(tmp)
```

### Coverage

```{r, eval = FALSE}
set.seed(123)
res <- eb_boot_sim(beta = c(0.25, 0.5, 0.75, 1, 1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5))
save(res, file = "increasing.rds")
```

```{r, echo=FALSE}
load("/Users/loganharris/github/lasso-boot/web/data/increasing.rds")
```


#### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov)
```

#### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage)
```
