---
title: "EB CI Simple Example"
author: "Logan Harris"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This serves as a proof of concept that the method I am using for finding a confidence interval is indeed working... but that the main issue we run into is dealing with the numerical instability of the posterior.

I can't remember exactly how Patrick did this (stochastic or not) but I think this is sufficient for now especially seeing even this breaks down.

Editorial note: Finish this later by adding a range of example using different rng and a spectrum of sample sizes. It would also be nice here to have plot outputs of the prior and posteriors as examples. Or this may be better suited for the bayes simple so we can see it in a place where we are actually fitting the lasso.


```{r}
ll <- function(beta, mean, sigma, n = 30) {
  # Compute the log-likelihood(s)
  sapply(beta, function(x) n*log(dnorm(mean - x, mean = 0, sd = sigma)))
}

dlaplace <- function(x, rate = 1) {
  dexp(abs(x), rate) / 2
}

density_function <- function(x, rate, mean, sigma, n = 30, multiplier = 1) {

  prior <- log(dlaplace(x, rate = rate))
  llik <- ll(beta = x, mean = mean, sigma = sigma, n = n)
  return(exp(prior + llik + sqrt(2)*n + log(multiplier)))

}

density_function_normalized <- function(x, rate, mean, sigma, n = 30, normalizer, multiplier = 1) {

  prior <- log(dlaplace(x, rate = rate))
  llik <- ll(beta = x, mean = mean, sigma = sigma, n = n)
  return(exp(prior + llik - log(normalizer) + sqrt(2)*n + log(multiplier)))

}

obj_simple <- function(beta, p, mean, sigma, rate, bounds, n = 30, multiplier = 1) {

  denom <- integrate(
    density_function, lower = bounds[1], upper = bounds[2], rate, mean, sigma, n, multiplier
  )$value

  if (p > .5) {
    prob <- integrate(
      density_function_normalized, lower = bounds[1], upper = beta, rate, mean, sigma, n, normalizer = denom, multiplier
    )$value
  } else {
    prob <- integrate(
      density_function_normalized, lower = beta, upper = bounds[2], rate, mean, sigma, n, normalizer = denom, multiplier
    )$value
    prob <- 1 - prob
  }

  return(p - prob)

}

post_quant <- function(sig, post_mode, mean = 0, sigma = 1, rate = 1, n = 30, plot = FALSE) {
  
  mltplyr <- 1 / density_function(post_mode, rate, mean, sigma, n, multiplier = 1)
  
  ## Determine the normalizing constant
  denom <- integrate(
    density_function, lower = -Inf, upper = Inf,
    rate = rate, mean = mean, sigma = sigma, n = n, multiplier = mltplyr
  )$value
  
  ## Find the largest density, used for determining bounds of integration / plotting
  ymode <- density_function_normalized(post_mode, rate, mean, sigma, n, denom, multiplier = mltplyr)
  ## Determine bounds
  step <- .01
  curr <- step
  while (TRUE) {
    xvals <- post_mode + c(-1, 1)*curr
    yvals <- density_function_normalized(xvals, rate, mean, sigma, n, denom, multiplier = mltplyr)

    if (all(yvals < (ymode / 100))) {break} else {curr <- curr + step}
  }

  ## Redetermine normalizing constant based on new bounds
  denom <- integrate(
    density_function, lower = post_mode - curr, upper = post_mode + curr,
    rate = rate, mean = mean, sigma = sigma, n = n, multiplier = mltplyr
  )$value
  

  ## Determine the bounds
  p <- sig + ((1 - sig) / 2)
  lower <- uniroot(obj_simple, c(post_mode - curr, post_mode + curr), p, mean, sigma, rate, c(post_mode - curr, post_mode + curr), n, multiplier = mltplyr)
  upper <- uniroot(obj_simple, c(post_mode - curr, post_mode + curr), 1 - p, mean, sigma, rate, c(post_mode - curr, post_mode + curr), n, multiplier = mltplyr)
  
  bounds <- c(lower$root, upper$root)
  
  ## Produce a plot of the posterior, posterior mode, prior, and likelihood
  if (plot) {
    xvals <- seq(post_mode - curr, post_mode + curr, by = .01)
    yvals <- density_function_normalized(xvals, rate, mean, sigma, n, denom, multiplier = mltplyr)
    priory <- dlaplace(xvals, rate = rate) * (ymode / dlaplace(0, rate = rate))
    liky <- exp(ll(beta = xvals, mean = mean, sigma = sigma, n = n))
    liky <- (liky / max(liky)) * ymode
    plot(xvals, yvals, type = "l", lty = 1)
    lines(xvals, priory, col = "blue", lty = 2)
    lines(xvals, liky, col = "blue", lty = 2)
    abline(v = post_mode, col = "red")
    abline(v = bounds, col = "red", lty = 2)
  }
  
  
  return(bounds)

}
```




```{r}
post_quant(sig = .8, post_mode = 0, mean = 0, n = 30, rate = 1, plot = TRUE)
```

```{r}
post_quant(sig = .8, post_mode = 0, mean = 0, n = 300, rate = 1, plot = TRUE)
```


```{r}
post_quant(sig = .8, post_mode = 0, mean = 0, n = 300, rate = 10, plot = TRUE)
```
