---
title: "Comparing Bayesian Methods"
runtime: shiny
output:
  html_document:
    code_folding: show
---

```{r setup, child = 'web/_include/setup.rmd'}
```


```{r}
source("./R/bayes_functions_fast.R")

library(TeachingDemos)
my_seed <- char2seed("Logan M. Harris")
```

# One Covariate

## Beta = 0

### Single Interval

#### Original

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, nboot = 100, type = "original", time = TRUE)

print(c(mean(tmp$lower), mean(tmp$upper)))
```

#### Univariate

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, nboot = 100, type = "univariate", time = TRUE)

print(c(mean(tmp$lower), mean(tmp$upper)))
```

### Coverage

#### Original


```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "original")
mean(res$overall_cov)
```

```{r, echo=FALSE}
save(res, file = "./web/data/bayes_simple/beta0_original_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta0_original_cv1.rds")
mean(res$overall_cov)
```

#### Univariate

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "univariate")
mean(res$overall_cov)
```

```{r}
save(res, file = "./web/data/bayes_simple/beta0_univariate_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta0_univariate_cv1.rds")
mean(res$overall_cov)
```


## Beta = 3

### Single Interval

#### Original

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, nboot = 100, type = "original", time = TRUE)

print(c(mean(tmp$lower), mean(tmp$upper)))
```

#### Univariate

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, nboot = 100, type = "univariate", time = TRUE)

print(c(mean(tmp$lower), mean(tmp$upper)))
```

### Coverage

#### Original

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "original")
mean(res$overall_cov)
```

```{r, echo=FALSE}
save(res, file = "./web/data/bayes_simple/beta3_original_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta3_original_cv1.rds")
mean(res$overall_cov)
```

#### Univariate

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "univariate")
mean(res$overall_cov)
```

```{r, echo=FALSE}
save(res, file = "./web/data/bayes_simple/beta3_univariate_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta3_univariate_cv1.rds")
mean(res$overall_cov)
```

# Many Covariates

## p = 60, n = 100

### Single Example

#### Original

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "original", time = TRUE)
plot_boot(tmp)
```

#### Univariate

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "univariate", time = TRUE)
plot_boot(tmp)
```

### Coverage

#### Original

```{r, eval = FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "original")
```

```{r, echo=FALSE}
save(res, file = "./web/data/bayes_simple/many_original_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/many_original_cv1.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

#### Univariate

```{r, eval = FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "univariate")
save(res, file = "./web/data/bayes_simple/many_univariate_cv1.rds")
```

```{r, echo=FALSE}
save(res, file = "./web/data/bayes_simple/many_univariate_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/many_univariate_cv1.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

# Speed of Univariate

```{r, eval = FALSE}
set.seed(my_seed)
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), b = 2, p = 6000, n = 100, nboot = 100, type = "normal", time = TRUE)
```

Generate data: 46.468 sec elapsed
Cross Validation: 0.701 sec elapsed
Bootstrapping: 1046.003 sec elapsed
Overall: 1093.173 sec elapsed

# Real Data

## Rhee2006

### Pre-process data

- Remove constant and perfectly colinear columns

```{r}
dat <- readData(Rhee2006)
dup <- duplicated(t(dat$X))
const <- apply(dat$X, 2, function(x) length(unique(x)) == 1)
dat$X <- dat$X[,!dup & !const]
```

### Perform Bootstrap

```{r}
set.seed(my_seed)
rhee <- eb_boot(dat = dat, type = "univariate", nboot = 200, time = TRUE)
```

```{r}
plot_boot(rhee, n = 60)
```

```{r}
lowers <- apply(rhee[["lower"]], 2, mean, na.rm = TRUE)
uppers <- apply(rhee[["upper"]], 2, mean, na.rm = TRUE)
sum(sign(lowers) * sign(uppers) == 1)
```

## pollution

```{r}
dat <- readData(pollution)
dat$X <- ncvreg::std(dat$X)

set.seed(my_seed)
pollution <- eb_boot(dat = dat, type = "univariate", time = TRUE)
```

```{r}
plot_boot(pollution)
```

## whoari

```{r}
dat <- readData(whoari)
dat$X <- ncvreg::std(dat$X)

set.seed(my_seed)
whoari <- eb_boot(dat = dat, type = "univariate", time = TRUE)
```

```{r}
plot_boot(whoari)
```


```{r}
t(1:4 * t(matrix(1, nrow = 4, ncol = 4)))

rep(1, 5) - t(1:4 * t(matrix(1, nrow = 5, ncol = 4))) 
```

