---
title: "Comparing Bayesian Methods"
runtime: shiny
output:
  html_document:
    code_folding: hide
---

```{r setup, child = 'web/_include/setup.rmd'}
```


```{r}
source("./R/bayes_functions_fast.R")

library(TeachingDemos)
my_seed <- char2seed("Logan M. Harris")
```

# One Covariate

## Beta = 0

### Single Interval

#### Original

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, nboot = 100, type = "original")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

#### Univariate

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, nboot = 100, type = "univariate")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

#### Normal

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, nboot = 100, type = "normal")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

#### Cadillac

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, nboot = 100, type = "cadillac")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

### Coverage

#### Original


```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "original")
save(res, file = "./web/data/bayes_simple/beta0_original_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta0_original_cv1.rds")
mean(res$overall_cov)
```

#### Univariate

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "univariate")
save(res, file = "./web/data/bayes_simple/beta0_univariate_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta0_univariate.rds")
mean(res$overall_cov)
```

#### Normal

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "normal")
save(res, file = "./web/data/bayes_simple/beta0_normal_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta0_normal_cv1.rds")
mean(res$overall_cov)
```

#### Cadillac

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "cadillac")
save(res, file = "./web/data/bayes_simple/beta0_cadillac_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta0_cadillac.rds")
mean(res$overall_cov)
```

## Beta = 3

### Single Interval

#### Original

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, nboot = 100, type = "original")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

#### Univariate

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, nboot = 100, type = "univariate")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```


#### Normal

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, nboot = 100, type = "normal")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

#### Cadillac

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, nboot = 100, type = "cadillac")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

### Coverage

#### Original

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "original")
save(res, file = "./web/data/bayes_simple/beta3_original_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta3_original_cv1.rds")
mean(res$overall_cov)
```

#### Univariate

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "univariate")
save(res, file = "./web/data/bayes_simple/beta3_univariate_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta3_univariate.rds")
mean(res$overall_cov)
```

#### Normal

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "normal")
save(res, file = "./web/data/bayes_simple/beta3_normal_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta3_normal_cv1.rds")
mean(res$overall_cov)
```

#### Cadillac

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "cadillac")
save(res, file = "./web/data/bayes_simple/beta3_cadillac_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta3_cadillac_cv1.rds")
mean(res$overall_cov)
```

# Many Covariates

## p = 60, n = 100

### Single Example

#### Original

```{r}
set.seed(my_seed)
tic()
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "original")
toc()
plot_boot(tmp)
```

#### Univariate

```{r}
set.seed(my_seed)
tic()
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "univariate")
toc()
plot_boot(tmp)
```

#### Normal

```{r}
set.seed(my_seed)
tic()
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "normal")
toc()
plot_boot(tmp)
```

#### Cadillac

```{r}
set.seed(my_seed)
tic()
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "cadillac")
toc()
plot_boot(tmp)
```

### Coverage

#### Original

```{r, eval = FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "original")
save(res, file = "./web/data/bayes_simple/many_original_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/many_original_cv1.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

#### Univariate

```{r, eval = FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "univariate")
save(res, file = "./web/data/bayes_simple/many_univariate_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/many_univariate_cv1.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

#### Normal

```{r, eval = FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "normal")
save(res, file = "./web/data/bayes_simple/many_normal_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/many_normal_cv1.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

#### Cadillac

```{r, eval = FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "cadillac")
save(res, file = "./web/data/bayes_simple/many_cadillac_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/many_cadillac_cv1.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

# Speed of Normal

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), b = 2, p = 60, n = 100, nboot = 100, type = "normal")
toc()
```

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), b = 2, p = 600, n = 100, nboot = 100, type = "normal")
toc()
```

# Debiasing?

- Normal is still trash 

## Univariate

### n > p

```{r, eval = FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "univariate", debias = TRUE)
save(res, file = "./web/data/bayes_simple/many_univariate_debias_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/many_univariate_debias_cv1.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

## Normal

### Single

```{r}
set.seed(my_seed)
tic()
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "normal", debias = TRUE)
toc()
plot_boot(tmp)
```

### n > p

```{r, eval = FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "normal", debias = TRUE)
save(res, file = "./web/data/bayes_simple/many_normal_debias_cv1_nep.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/many_normal_debias_cv1_nep.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

## Cadillac

```{r}
set.seed(my_seed)
tic()
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "cadillac", debias = TRUE)
toc()
plot_boot(tmp)
```

### n > p

```{r, eval = FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "cadillac", debias = TRUE)
save(res, file = "./web/data/bayes_simple/many_cadillac_debias_cv1_nep.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/many_cadillac_debias_cv1_nep.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

# Real Data

## Rhee2006

```{r}
dat <- readData(Rhee2006)
dup <- duplicated(t(dat$X))
const <- apply(dat$X, 2, function(x) length(unique(x)) == 1)
dat$X <- dat$X[,!dup & !const]

set.seed(my_seed)
tic()
rhee <- eb_boot(dat = dat, type = "univariate", nboot = 200)
toc()
```

```{r}
plot_boot(rhee, n = 60)
```

```{r}
lowers <- apply(rhee[["lower"]], 2, mean, na.rm = TRUE)
uppers <- apply(rhee[["upper"]], 2, mean, na.rm = TRUE)
sum(sign(lowers) * sign(uppers) == 1)
```

## pollution

```{r}
dat <- readData(pollution)
dat$X <- ncvreg::std(dat$X)
set.seed(my_seed)
tic()
pollution <- eb_boot(dat = dat, type = "univariate")
toc()
```

```{r}
plot_boot(pollution)
```

## whoari

```{r}
dat <- readData(whoari)
dat$X <- ncvreg::std(dat$X)
set.seed(my_seed)
tic()
whoari <- eb_boot(dat = dat, type = "univariate")
toc()
```

```{r}
plot_boot(whoari, n = 66)
```
