---
title: "Comparing Bayesian Methods"
runtime: shiny
output:
  html_document:
    code_folding: hide
---

```{r setup, child = 'web/_include/setup.rmd'}
```


```{r}
source("./R/bayes_functions.R")

library(TeachingDemos)
my_seed <- char2seed("Logan M. Harris")
```

This now focuses on:

1) Comparing the different methods discussed
2) Even more so on the normal approximation approach

# One Covariate

## Beta = 0

### Single Interval

#### Original

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, nboot = 100, type = "original")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

#### Univariate

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, nboot = 100, type = "univariate")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

#### Normal

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, nboot = 100, type = "normal")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

#### Cadillac

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, nboot = 100, type = "cadillac")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

### Coverage

#### Original


```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "original")
save(res, file = "./web/data/bayes_simple/beta0_original.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta0_original.rds")
mean(res$overall_cov)
```

#### Univariate

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "univariate")
save(res, file = "./web/data/bayes_simple/beta0_univariate.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta0_univariate.rds")
mean(res$overall_cov)
```

#### Normal

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "normal")
save(res, file = "./web/data/bayes_simple/tst.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta0_normal.rds")
mean(res$overall_cov)
```

#### Cadillac

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "cadillac")
save(res, file = "./web/data/bayes_simple/beta0_cadillac.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta0_cadillac.rds")
mean(res$overall_cov)
```

## Beta = 3

### Single Interval

#### Original

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, nboot = 100, type = "original")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

#### Univariate

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, nboot = 100, type = "univariate")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```


#### Normal

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, nboot = 100, type = "normal")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

#### Cadillac

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, nboot = 100, type = "cadillac")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

### Coverage

#### Original

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "original")
save(res, file = "./web/data/bayes_simple/beta3_original.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta3_original.rds")
mean(res$overall_cov)
```

#### Univariate

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "univariate")
save(res, file = "./web/data/bayes_simple/beta3_univariate.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta3_univariate.rds")
mean(res$overall_cov)
```

#### Normal

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "normal")
save(res, file = "./web/data/bayes_simple/beta3_normal.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta3_normal.rds")
mean(res$overall_cov)
```

#### Cadillac

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "cadillac")
save(res, file = "./web/data/bayes_simple/beta3_cadillac.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta3_cadillac.rds")
mean(res$overall_cov)
```

# Many Covariates

## p = 60, n = 100

### Single Example

#### Original

```{r}
set.seed(my_seed)
tic()
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "original")
toc()
plot_boot(tmp)
```

#### Univariate

```{r}
set.seed(my_seed)
tic()
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "univariate")
toc()
plot_boot(tmp)
```

#### Normal

```{r}
set.seed(my_seed)
tic()
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "normal")
toc()
plot_boot(tmp)
```

#### Cadillac

```{r}
set.seed(my_seed)
tic()
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "cadillac")
toc()
plot_boot(tmp)
```

### Coverage

#### Original

```{r, eval = FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "original")
save(res, file = "./web/data/bayes_simple/many_original.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/many_original.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

#### Univariate

```{r, eval = FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "univariate")
save(res, file = "./web/data/bayes_simple/many_univariate.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/many_univariate.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

#### Normal

```{r, eval = FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "normal")
save(res, file = "./web/data/bayes_simple/many_normal.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/many_normal.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

#### Normal vs. Laplace

```{r}
rates <- c(1)
sigma2 <- 2 / (rates^2)

for (i in 1:length(sigma2)) {
  xvals <- seq(-sqrt(sigma2[i])*4, sqrt(sigma2[i])*4, by = sqrt(sigma2[i])/10)
  ynorm <- dnorm(xvals, 0, sqrt(sigma2[i]))
  ylaplace <- dlaplace(xvals, rates[i])
  plot(xvals, ylaplace, type = "l", col = "red")
  lines(xvals, ynorm, col = "blue")
}
```

```{r}
for (i in 1:length(sigma2)) {
  xvals <- seq(-sqrt(sigma2[i])*4, sqrt(sigma2[i])*4, by = sqrt(sigma2[i])/10)
  ynorm <- dnorm(xvals, 0, sqrt(sigma2[i])) * dnorm(xvals, 3, 1) / sum(dnorm(xvals, 0, sqrt(sigma2[i])) * dnorm(xvals, 3, 1) )
  ylaplace <- dlaplace(xvals, rates[i]) * dnorm(xvals, 3, 1) / sum(dlaplace(xvals, rates[i]) * dnorm(xvals, 3, 1))
  plot(xvals, ynorm, type = "l", col = "blue")
  lines(xvals, ylaplace, col = "red")
  abline(v = xvals[which.max(ynorm)], col = "blue")
  abline(v = xvals[which.max(ylaplace)], col = "red")
}
```

#### Cadillac

```{r, eval = FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "cadillac")
save(res, file = "./web/data/bayes_simple/many_cadillac.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/many_cadillac.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

# Speed of Normal

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), b = 2, p = 60, n = 100, nboot = 100, type = "normal")
toc()
```

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), b = 2, p = 600, n = 100, nboot = 100, type = "normal")
toc()
```

```{r}
# # 1179.776 sec elapsed
# tic()
# set.seed(my_seed)
# tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), b = 2, p = 60000, n = 100, nboot = 100, type = "normal")
# toc()
# 
# tic()
# dat <- genDataABN(beta = c(2, 1, 0.5, -2, -1, -0.5), p = 600, a = 6, b = 2, n = 100)
# toc()
```

# Debiasing?

## Univariate

### Single Covariate (Beta = 0)

#### Single Example

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, nboot = 100, type = "univariate", debias = TRUE)
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

#### Coverage

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "univariate", debias = TRUE)
save(res, file = "./web/data/bayes_simple/beta0_univariate_debias.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta0_univariate_debias.rds")
mean(res$overall_cov)
```

### Single Covariate (Beta = 3)

#### Single Example

```{r}
tic()
set.seed(my_seed)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, nboot = 100, type = "univariate", debias = TRUE)
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

#### Coverage

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "univariate", debias = TRUE)
save(res, file = "./web/data/bayes_simple/beta3_univariate_debias.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta3_univariate_debias.rds")
mean(res$overall_cov)
```

### n > p

```{r, eval = FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "univariate", debias = TRUE)
save(res, file = "./web/data/bayes_simple/many_univariate_debias.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/many_univariate_debias.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```
