---
title: "Comparing Bayesian Methods"
runtime: shiny
output:
  html_document:
    code_folding: hide
---

```{r setup, child = 'web/_include/setup.rmd'}
```


```{r}
source("./R/bayes_functions.R")
```

This now focuses on:

1) Comparing the different methods discussed
2) Even more so on the normal approximation approach

# One Covariate

## Beta = 0

### Single Interval

#### Original

```{r}
tic()
set.seed(12345)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, niter = 100, type = "original")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

#### Normal

```{r}
tic()
set.seed(12345)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, niter = 100, type = "normal")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

#### Cadillac

```{r}
tic()
set.seed(12345)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, niter = 100, type = "cadillac")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

### Coverage

#### Original

```{r, eval=FALSE}
set.seed(12345)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, niter = 100, nboot = 100)
save(res, file = "/Users/loganharris/github/lasso-boot/web/data/beta0_cov_original.rds")
```

```{r, echo=FALSE}
load("/Users/loganharris/github/lasso-boot/web/data/beta0_cov_original.rds")
mean(res$overall_cov)
```

#### Normal

```{r, eval=FALSE}
set.seed(12345)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, niter = 100, nboot = 100, type = "normal")
save(res, file = "/Users/loganharris/github/lasso-boot/web/data/beta0_cov_normal.rds")
```

```{r, echo=FALSE}
load("/Users/loganharris/github/lasso-boot/web/data/beta0_cov_normal.rds")
mean(res$overall_cov)
```

#### Cadillac

```{r, eval=FALSE}
set.seed(12345)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, niter = 100, nboot = 100, type = "cadillac")
save(res, file = "/Users/loganharris/github/lasso-boot/web/data/beta0_cov_cadillac.rds")
```

```{r, echo=FALSE}
load("/Users/loganharris/github/lasso-boot/web/data/beta0_cov_cadillac.rds")
mean(res$overall_cov)
```

## Beta = 3

### Single Interval

#### Original

```{r}
tic()
set.seed(12345)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, niter = 100, type = "original")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

#### Normal

```{r}
tic()
set.seed(12345)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, niter = 100, type = "normal")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

#### Cadillac

```{r}
tic()
set.seed(12345)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, niter = 100, type = "cadillac")
print("Mean: ")
print(c(mean(tmp$lower), mean(tmp$upper)))
print("Median: ")
print(c(median(tmp$lower), median(tmp$upper)))
toc()
```

### Coverage

#### Original

```{r, eval=FALSE}
set.seed(12345)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, niter = 100, nboot = 100)
save(res, file = "/Users/loganharris/github/lasso-boot/web/data/beta3_cov_original.rds")
```

```{r, echo=FALSE}
load("/Users/loganharris/github/lasso-boot/web/data/beta3_cov_original.rds")
mean(res$overall_cov)
```

#### Normal

```{r, eval=FALSE}
set.seed(12345)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, niter = 100, nboot = 100, type = "normal")
save(res, file = "/Users/loganharris/github/lasso-boot/web/data/beta3_cov_normal.rds")
```

```{r, echo=FALSE}
load("/Users/loganharris/github/lasso-boot/web/data/beta3_cov_normal.rds")
mean(res$overall_cov)
```

#### Cadillac

```{r, eval=FALSE}
set.seed(12345)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, niter = 100, nboot = 100, type = "cadillac")
save(res, file = "/Users/loganharris/github/lasso-boot/web/data/beta3_cov_cadillac.rds")
```

```{r, echo=FALSE}
load("/Users/loganharris/github/lasso-boot/web/data/beta3_cov_cadillac.rds")
mean(res$overall_cov)
```

# Many Covariates

## p = 60, n = 100

### Single Example

#### Original

```{r}
set.seed(12345)
tic()
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "original")
toc()
plot_boot(tmp)
```

#### Normal

```{r}
set.seed(12345)
tic()
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "normal")
toc()
plot_boot(tmp)
```

#### Cadillac

```{r}
set.seed(12345)
tic()
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "cadillac")
toc()
plot_boot(tmp)
```

### Coverage

#### Original

```{r, eval = FALSE}
set.seed(12345)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5))
save(res, file = "/Users/loganharris/github/lasso-boot/web/data/many_simple_original.rds")
```

```{r, echo=FALSE}
load("/Users/loganharris/github/lasso-boot/web/data/many_simple_original.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

#### Normal

```{r, eval = FALSE}
set.seed(12345)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "normal")
save(res, file = "/Users/loganharris/github/lasso-boot/web/data/many_simple_normal.rds")
```

```{r, echo=FALSE}
load("/Users/loganharris/github/lasso-boot/web/data/many_simple_normal.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

# Speed of Normal

```{r}
tic()
set.seed(12345)
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), b = 2, p = 60, n = 100, niter = 100, type = "normal")
toc()
```

```{r}
tic()
set.seed(12345)
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), b = 2, p = 600, n = 100, niter = 100, type = "normal")
toc()
```

```{r}
# 1179.776 sec elapsed
# tic()
# set.seed(12345)
# tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), b = 2, p = 6000, n = 100, niter = 100, type = "normal")
# toc()
```




