---
title: "EB Bootstrap Methods - CV Once"
output:
  html_document:
    code_folding: show
---

```{r setup, child = 'web/_include/setup.rmd'}
```


```{r}
source("./R/bayes_functions.R")

my_seed <- 189807771
```

# One Covariate

## Beta = 0

### Single Interval

#### Original

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, nboot = 100, type = "original", time = TRUE)

int_b0_O <- c(mean(tmp$lower), mean(tmp$upper))
```

#### Univariate

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, nboot = 100, type = "univariate", time = TRUE)

(int_b0_U <- c(mean(tmp$lower), mean(tmp$upper)))
```

[1] -0.6897276 -0.1468678

### Coverage

#### Original


```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "original")
cov_b0_O <- mean(res$overall_cov)
```

```{r, eval=FALSE, echo = FALSE}
save(res, file = "./web/data/bayes_simple/beta0_original_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta0_original_cv1.rds")
cov_b0_O <- mean(res$overall_cov)
```

#### Univariate

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "univariate")
cov_b0_U <- mean(res$overall_cov)
```

```{r, eval = FALSE, echo = FALSE}
save(res, file = "./web/data/bayes_simple/beta0_univariate_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta0_univariate_cv1.rds")
cov_b0_U <- mean(res$overall_cov)
```

### Comparison

```{r}
tbl <- data.frame("Original" = c(int_b0_O, cov_b0_O), "Univariate" = c(int_b0_U, cov_b0_U))
rownames(tbl) <- c("Lower (Single)", "Upper (Single)", "Coverage (100 Simulations)")
tbl %>% kbl() %>% kable_material(c("striped", "hover"))
```

## Beta = 3

### Single Interval

#### Original

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, nboot = 100, type = "original", time = TRUE)

int_b3_O <- c(mean(tmp$lower), mean(tmp$upper))
```

#### Univariate

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, nboot = 100, type = "univariate", time = TRUE)

int_b3_U <- c(mean(tmp$lower), mean(tmp$upper))
```

### Coverage

#### Original

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "original")
cov_b3_O <- mean(res$overall_cov)
```

```{r, eval=FALSE, echo = FALSE}
save(res, file = "./web/data/bayes_simple/beta3_original_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta3_original_cv1.rds")
cov_b3_O <- mean(res$overall_cov)
```

#### Univariate

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "univariate")
cov_b3_U <- mean(res$overall_cov)
```

```{r, echo=FALSE, eval = FALSE}
save(res, file = "./web/data/bayes_simple/beta3_univariate_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta3_univariate_cv1.rds")
cov_b3_U <-mean(res$overall_cov)
```

### Comparison

```{r}
tbl <- data.frame("Original" = c(int_b3_O, cov_b3_O), "Univariate" = c(int_b3_U, cov_b3_U))
rownames(tbl) <- c("Lower", "Upper", "Coverage")
tbl %>% kbl() %>% kable_material(c("striped", "hover"))
```

# Many Covariates

## p = 60, n = 100

### Single Example

#### Original

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "original", time = TRUE)

plot_boot(tmp)
```

#### Univariate

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "univariate", time = TRUE)

plot_boot(tmp, n = 60)
```


### Coverage

#### Univariate

```{r, eval = FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "univariate", interval_type = "HPD")
```

```{r, echo=FALSE, eval = FALSE}
save(res, file = "./web/data/bayes_simple/many_univariate_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/many_univariate_cv1.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

# Real Data

## Rhee2006

### Pre-process data

- Remove constant and perfectly co-linear columns

```{r}
dat <- readData(Rhee2006)
dup <- duplicated(t(dat$X))
const <- apply(dat$X, 2, function(x) length(unique(x)) == 1)
dat$X <- dat$X[,!dup & !const]
# dat$X <- std(dat$X)
```

### Perform Bootstrap / plot

```{r}
set.seed(my_seed)
rhee <- eb_boot(dat = dat, type = "univariate", nboot = 200, time = TRUE)

plot_boot(rhee, n = 20)
```

Number intervals not containing 0:

```{r}
lowers <- apply(rhee[["lower"]], 2, mean, na.rm = TRUE)
uppers <- apply(rhee[["upper"]], 2, mean, na.rm = TRUE)
sum(sign(lowers) * sign(uppers) == 1)
```


## pollution

```{r}
dat <- readData(pollution)
# dat$X <- ncvreg::std(dat$X)

set.seed(my_seed)
pollution <- eb_boot(dat = dat, type = "univariate", time = TRUE)

plot_boot(pollution)
```
## whoari

```{r}
dat <- readData(whoari)

set.seed(my_seed)
whoari <- eb_boot(dat = dat, type = "univariate", time = TRUE)

plot_boot(whoari, n = 20)
```

# Comparison Methods

## whoari

```{r}
dat <- readData(whoari)
dat$X <- std(dat$X)
```


### Selective Inference

- Tends to produce infinite values

```{r}
library(selectiveInference)
library(glmnet)

set.seed(my_seed)
cv_res <- cv.glmnet(dat$X, dat$y, standardize = FALSE)
(lam <- cv_res$lambda.min)

fit <- cv_res$glmnet.fit
b <- coef(fit, s = lam)[-1]
sh <- estimateSigma(dat$X, dat$y)$sigmahat  # About 0.4 or 0.45
res <- fixedLassoInf(dat$X, dat$y, b, lam*length(dat$y), sigma=sh, alpha = .2)
bb <- res$vmat %*% dat$y
B <- cbind(bb, res$ci, res$pv)
rownames(B) <- names(res$vars)
B <- B[is.finite(B[,2]) & is.finite(B[,3]),-4]
si_whoari <- B %>%
  data.frame(method = "Selective Inference", variable = rownames(B)) %>%
  rename(estimate = X1, lower = X2, upper = X3)
# B <- B[order(desc(abs(B[,1]))),][1:30,]
# CIplot(B, sort=FALSE, mar=c(4, 5, 1, 5), xlab=expression(beta))
```

## HDI

- Seems slow / fragile so far (error on Rhee)
- There is also a non-bootstrap version I can consider

```{r}
library(hdi)

fit.lasso.allinfo <- boot.lasso.proj(dat$X, dat$y, return.bootdist = TRUE)
ci_hdi <- confint(fit.lasso.allinfo, level = 0.8)

hdi_whoari <- ci_hdi %>%
  data.frame(method = "BLP", variable = rownames(ci_hdi)) %>%
  mutate(estimate = (lower + upper) / 2)
```

## Lasso Boot

```{r}
set.seed(my_seed)
whoari <- eb_boot(dat = dat, type = "univariate", time = FALSE)

lassoboot_whoari <- boot_ci(whoari)
```

## Comparison

```{r}
ci_df <- bind_rows(si_whoari, hdi_whoari, lassoboot_whoari)

gg <- plot_ci_comparison(ci_df)
gg + coord_cartesian(xlim=c(-.25, .5))
```


## Generated Data

```{r}
set.seed(my_seed)
dat <- genDataABN(beta = c(2, 1, 0.5, -2, -1, -0.5), p = 60, a = 6, b = 2, n = 100)
dat$X <- std(dat$X)
```

### Selective Inference

```{r}
set.seed(my_seed)
cv_res <- cv.glmnet(dat$X, dat$y, standardize = FALSE)
lam <- cv_res$lambda.min

fit <- cv_res$glmnet.fit
b <- coef(fit, s = lam)[-1]
sh <- estimateSigma(dat$X, dat$y)$sigmahat
res <- fixedLassoInf(dat$X, dat$y, b, lam*length(dat$y), sigma=sh, alpha = .2)
bb <- res$vmat %*% dat$y
B <- cbind(bb, res$ci, res$pv)
rownames(B) <- names(res$vars)
B <- B[is.finite(B[,2]) & is.finite(B[,3]),-4]
si_abn <- B %>%
  data.frame(method = "Selective Inference", variable = rownames(B)) %>%
  rename(estimate = X1, lower = X2, upper = X3)
```

## HDI

```{r}
fit.lasso.allinfo <- boot.lasso.proj(dat$X, dat$y, return.bootdist = TRUE)
ci_hdi <- confint(fit.lasso.allinfo, level = 0.8)

hdi_abn <- ci_hdi %>%
  data.frame(method = "BLP", variable = rownames(ci_hdi)) %>%
  mutate(estimate = (lower + upper) / 2)
```

## Lasso Boot

```{r}
set.seed(my_seed)
abn <- eb_boot(dat = dat, type = "univariate", time = FALSE)

lassoboot_abn <- boot_ci(abn)
```

## Comparison

```{r}
ci_df <- bind_rows(si_abn, hdi_abn, lassoboot_abn)

gg <- plot_ci_comparison(ci_df)
gg + coord_cartesian(xlim=c(-3, 3))
```

