---
title: "EB Bootstrap Methods - CV Once"
output:
  html_document:
    code_folding: show
---

```{r setup, child = 'web/_include/setup.rmd'}
```


```{r}
source("./R/bayes_functions.R")

library(TeachingDemos)
my_seed <- char2seed("Logan M. Harris")
```

# One Covariate

## Beta = 0

### Single Interval

#### Original

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, nboot = 100, type = "original", time = TRUE)

int_b0_O <- c(mean(tmp$lower), mean(tmp$upper))
```

#### Univariate

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = 0, p = 1, b = 0, n = 30, nboot = 100, type = "univariate", time = TRUE)

int_b0_U <- c(mean(tmp$lower), mean(tmp$upper))
```

### Coverage

#### Original


```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "original")
cov_b0_O <- mean(res$overall_cov)
```

```{r, echo=FALSE}
save(res, file = "./web/data/bayes_simple/beta0_original_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta0_original_cv1.rds")
cov_b0_O <- mean(res$overall_cov)
```

#### Univariate

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 0, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "univariate")
cov_b0_U <- mean(res$overall_cov)
```

```{r, echo = FALSE}
save(res, file = "./web/data/bayes_simple/beta0_univariate_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta0_univariate_cv1.rds")
cov_b0_U <- mean(res$overall_cov)
```

### Comparison

```{r}
tbl <- data.frame("Original" = c(int_b0_O, cov_b0_O), "Univariate" = c(int_b0_U, cov_b0_U))
rownames(tbl) <- c("Lower (Single)", "Upper (Single)", "Coverage (100 Simulations)")
tbl %>% kbl() %>% kable_material(c("striped", "hover"))
```

## Beta = 3

### Single Interval

#### Original

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, nboot = 100, type = "original", time = TRUE)

int_b3_O <- c(mean(tmp$lower), mean(tmp$upper))
```

#### Univariate

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = 3, p = 1, b = 0, n = 30, nboot = 100, type = "univariate", time = TRUE)

int_b3_U <- c(mean(tmp$lower), mean(tmp$upper))
```

### Coverage

#### Original

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "original")
cov_b3_O <- mean(res$overall_cov)
```

```{r, echo=FALSE}
save(res, file = "./web/data/bayes_simple/beta3_original_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta3_original_cv1.rds")
cov_b3_O <- mean(res$overall_cov)
```

#### Univariate

```{r, eval=FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = 3, p = 1, b = 0, n = 30, nboot = 100, nsim = 100, type = "univariate")
cov_b3_U <-mean(res$overall_cov)
```

```{r, echo=FALSE}
save(res, file = "./web/data/bayes_simple/beta3_univariate_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/beta3_univariate_cv1.rds")
cov_b3_U <-mean(res$overall_cov)
```

### Comparison

```{r}
tbl <- data.frame("Original" = c(int_b3_O, cov_b3_O), "Univariate" = c(int_b3_U, cov_b3_U))
rownames(tbl) <- c("Lower", "Upper", "Coverage")
tbl %>% kbl() %>% kable_material(c("striped", "hover"))
```

# Many Covariates

## p = 60, n = 100

### Single Example

#### Original

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "original", time = TRUE)

plot_boot(tmp)
```

#### Univariate

```{r}
set.seed(my_seed)
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "univariate", time = TRUE)

plot_boot(tmp)
```


### Coverage

#### Original

```{r, eval = FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "original")
```

```{r, echo=FALSE}
save(res, file = "./web/data/bayes_simple/many_original_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/many_original_cv1.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

#### Univariate

```{r, eval = FALSE}
set.seed(my_seed)
res <- eb_boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), type = "univariate")
```

```{r, echo=FALSE}
save(res, file = "./web/data/bayes_simple/many_univariate_cv1.rds")
```

```{r, echo=FALSE}
load("./web/data/bayes_simple/many_univariate_cv1.rds")
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_cov)
hist(res$overall_cov, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$indiv_cov, 2, mean) , beta = res$truth)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

# Speed of Univariate

```{r, eval = FALSE}
set.seed(my_seed)
tmp <- eb_boot(beta = c(2, 1, 0.5, -2, -1, -0.5), b = 2, p = 6000, n = 100, nboot = 100, type = "cadillac", time = TRUE)
```

Generate data: 46.85 sec elapsed

Cross Validation: 1.131 sec elapsed

Bootstrapping: 1048.716 sec elapsed

Overall: 1096.699 sec elapsed

Cadillac: 2152.769 sec elapsed

Normal: 1097.472 sec elapsed

# Real Data

## Rhee2006

### Pre-process data

- Remove constant and perfectly colinear columns

```{r}
dat <- readData(Rhee2006)
dup <- duplicated(t(dat$X))
const <- apply(dat$X, 2, function(x) length(unique(x)) == 1)
dat$X <- dat$X[,!dup & !const]
```

### Perform Bootstrap / plot

```{r}
set.seed(my_seed)
rhee <- eb_boot(dat = dat, type = "univariate", nboot = 200, time = TRUE)

plot_boot(rhee, n = 60)
```

Number intervals not containing 0:

```{r}
lowers <- apply(rhee[["lower"]], 2, mean, na.rm = TRUE)
uppers <- apply(rhee[["upper"]], 2, mean, na.rm = TRUE)
sum(sign(lowers) * sign(uppers) == 1)
```

## pollution

```{r}
dat <- readData(pollution)
dat$X <- ncvreg::std(dat$X)

set.seed(my_seed)
pollution <- eb_boot(dat = dat, type = "univariate", time = TRUE)

plot_boot(pollution)
```

## whoari

```{r}
dat <- readData(whoari)
dat$X <- ncvreg::std(dat$X)

set.seed(my_seed)
whoari <- eb_boot(dat = dat, type = "univariate", time = TRUE)

plot_boot(whoari)
```

