---
title: "nvcreg implimentation"
author: "Logan Harris"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
---

```{r setup, child = 'web/_include/setup.rmd'}
```

```{r, eval=FALSE}
## install.packages("githubinstall")
## githubinstall::gh_install_packages("breheny/ncvreg", ref = "bootstrap")
```


# The posterior

## Set up

```{r}
dlaplace <- function(x, rate = 1, log = FALSE) {
  if (log) {
    dexp(abs(x), rate, log = TRUE) - log(2)
  } else {
    dexp(abs(x), rate) / 2 
  }
}
dlik <- function(x, z, sigma2, n, log = FALSE) {
  if (log) {
    -(n/2*sigma2)*(x - z)^2
  } else {
    exp(-(n/2*sigma2)*(x - z)^2)
  }
}
dpost <- function(x, z, sigma2, n, lambda, log = FALSE) {
  rate <- (lambda*n / sigma2)
  if (log) {
    return(dlaplace(x, rate = rate, log = TRUE) + dlik(x, z, sigma2, n, log = TRUE))
  } else {
    return(dlaplace(x, rate = rate) * dlik(x, z, sigma2, n))
  }
}
```

## lambda = 1, sigma2 = 1, n = 100 (posterior)

```{r}
zs <- c(0, .5, 1, 1.2, 1.5, 2)
lambda <- 1
sigma2 <- 1
n <- 100
x <- seq(-1, 1, by = .001)

for (z in zs) {
  dense <- dpost(x, z, sigma2, n, lambda)
  plot(x, dense, type = "l") 
}
```

## n = 10000 (log - posterior)

```{r}
n <- 10000
x <- seq(-1, 1, by = .01)

for (z in zs) {
  dense <- dpost(x, z, sigma2, n, lambda, log = TRUE)
  plot(x, dense, type = "l") 
}
```

# Comparison to Using Integrate (at lambda_max)

```{r}
set.seed(my_seed)
dat <- hdrm::genDataABN(n = 40, p = 60, a = 6, b = 2, beta = c(-2, -1, -0.5, 0.5, 1, 2))

lambda_max <- max(ncvreg:::find_thresh(std(dat$X), dat$y))
lambda_max <- lambda_max - lambda_max*.01
set.seed(my_seed)
boot_res <- boot.ncvreg(X = dat$X, y = dat$y, lambda = lambda_max)
ci_new <- ncvreg:::ci.boot.ncvreg(boot_res) %>%
  dplyr::select(variable, lower, upper)
```


```{r}
set.seed(my_seed)
tmp_orig <- eb_boot(dat = dat, type = "original", lambda = lambda_max)
names(tmp_orig) <- c("lowers", "uppers", "estimates")
ci_old <- ncvreg:::ci.boot.ncvreg(tmp_orig) %>%
  dplyr::select(variable, lower_old = lower, upper_old = upper)
```

```{r}
ci_new %>%
  left_join(ci_old, by = "variable")
```



# Supporting Functions

## Bootstrap Simulation

```{r}
boot_sim <- function(beta, n = 100, p = 60, b, nboot = 100, nsim = 100, progress = FALSE) {

  overall_cov <- numeric(nsim)
  indiv_cov <- matrix(nrow = nsim, ncol = p)

  if (progress) pb <- txtProgressBar(1, nsim, style = 3)

  for (iter in 1:nsim) {
    if (missing(b)) {
      dat <- gen_data(n = n, p = p, p1 = length(beta), beta = beta)  
    } else {
      dat <- genDataABN(n = n, p = p, a = length(beta), b = b, beta = beta)  
    }
    
    tbeta <- dat$beta
    boot <- boot.ncvreg(dat$X, dat$y, nboot = nboot, verbose = FALSE)
    ci <- ci.boot.ncvreg(boot)

    indiv_cov[iter,] <- tbeta >= ci$lower & tbeta <= ci$upper
    overall_cov[iter] <- mean(indiv_cov[iter,])

    if (progress) setTxtProgressBar(pb, iter)

  }

  return(list("overall_coverage" = overall_cov, "individual_coverage" = indiv_cov, "beta" = tbeta))

}
```

## Method Comparison

```{r}
plot_ci_comparison <- function(ci_df, nvars = 30) {

  plot_vars <- list()
  for (current_method in unique(ci_df$method)) {
    plot_vars[[current_method]] <- ci_df %>%
      filter(method == current_method) %>%
      dplyr::arrange(desc(abs(estimate))) %>%
      slice_head(n = nvars) %>%
      pull(variable)
  }
  plot_vars <- unique(unlist(plot_vars))

  plot_res <- ci_df %>%
    filter(variable %in% plot_vars) %>%
    dplyr::arrange(desc(abs(estimate)))

  plot_res$variable <- factor(plot_res$variable, levels = rev(plot_vars))

  gg <- plot_res %>%
    ggplot() +
    geom_errorbar(aes(xmin = lower, xmax = upper, y = variable, color = method), alpha = .6) +
    geom_point(aes(x = estimate, y = variable, color = method), alpha = .6) +
    theme_bw() +
    labs(y = "Variable", x = "Estimate")

  return(gg)

}
```

# One Covariate

## Beta = 0

### Single Interval

```{r}
set.seed(my_seed)
dat <- gen_data(n = 30, p = 1, beta = 0)
res <- boot.ncvreg(dat$X, dat$y, verbose = FALSE, seed = 1234)
ci.boot.ncvreg(res)
```


### Coverage

```{r}
set.seed(my_seed)
mean(boot_sim(beta = 0, n = 30, p = 1)$overall_coverage)
```

## Beta = 3

### Single Interval

```{r}
set.seed(my_seed)
dat <- gen_data(beta = 3, n = 30, p = 1, p1 = 1)
ci.boot.ncvreg(boot.ncvreg(dat$X, dat$y, verbose = FALSE))
```


### Coverage

```{r}
set.seed(my_seed)
mean(boot_sim(beta = 3, n = 30, p = 1)$overall_coverage)
```

# Many Covariates 

## p = 60, n = 100

### Single Example


```{r}
set.seed(my_seed)
dat <- genDataABN(beta = c(2, 1, 0.5, -2, -1, -0.5), n = 100, p = 60, a = 6, b = 2)
plot(boot.ncvreg(dat$X, dat$y, verbose = FALSE))
```


### Coverage

```{r}
set.seed(my_seed)
res <- boot_sim(beta = c(2, 1, 0.5, -2, -1, -0.5), b = 2)
```

##### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_coverage)
hist(res$overall_coverage, xlab = "Coverage", main ="")
```

##### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$individual_coverage, 2, mean) , beta = res$beta)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```

# Interval widths

```{r}
set.seed(my_seed)
dat <- hdrm::genDataABN(n = 100, p = 60, a = 6, b = 2, beta = c(-2, -1, -0.5, 0.5, 1, 2))
# dat <- gen_data(n = 100, p = 60, beta = c(-2, -1, -0.5, 0.5, 1, 2, rep(0, 54)))


lambda_max <- max(ncvreg:::find_thresh(std(dat$X), dat$y))
lambda_min <- lambda_max * 0.001
lambda_max <- lambda_max - lambda_max*.01
lambda_min <- lambda_min + lambda_min*.01
lambda_seq <- 10^(seq(log(lambda_max, 10), log(lambda_min, 10), length.out = 10))
```


## Variance = 1

```{r}
res <- list()
for (i in 1:length(lambda_seq)) {
  boot_res <- boot.ncvreg(X = dat$X, y = dat$y, lambda = lambda_seq[i], sigma2 = 1)
  res[[i]] <- ncvreg:::ci.boot.ncvreg(boot_res) %>%
    dplyr::mutate(width = upper - lower, lambda = lambda_seq[i]) %>%
    dplyr::select(variable, width, lambda, estimate) 
}

truth <- data.frame(variable = names(dat$beta), truth = as.character(abs(dat$beta)), sign = sign(dat$beta))
red_res <- res

do.call("rbind", red_res) %>%
  left_join(truth) %>%
  ggplot(aes(x = lambda, y = width * sign, color = truth)) +
  geom_point(alpha = .6) +
  scale_x_continuous(
    trans = 'log10' 
  ) +
  xlab("Lambda") + ylab("Interval Width") +
  theme_bw() +
  scale_color_discrete(name = expression(abs(beta)))


do.call("rbind", red_res) %>%
  left_join(truth) %>%
  ggplot(aes(x = lambda, y = width, color = truth)) +
  geom_jitter(alpha = .6, width = .05) +
  scale_x_continuous(
    trans = 'log10' 
  ) +
  xlab("Lambda") + ylab("Interval Width") +
  theme_bw() +
  scale_color_discrete(name = expression(abs(beta)))
```

## Variance estimated using CV

```{r}
res <- list()
for (i in 1:length(lambda_seq)) {
  boot_res <- boot.ncvreg(X = dat$X, y = dat$y, lambda = lambda_seq[i])
  res[[i]] <- ncvreg:::ci.boot.ncvreg(boot_res) %>%
    dplyr::mutate(width = upper - lower, lambda = lambda_seq[i]) %>%
    dplyr::select(variable, width, lambda, estimate) 
}

truth <- data.frame(variable = names(dat$beta), truth = as.character(abs(dat$beta)), sign = sign(dat$beta))
red_res <- res

do.call("rbind", red_res) %>%
  left_join(truth) %>%
  ggplot(aes(x = lambda, y = width * sign, color = truth)) +
  geom_point(alpha = .6) +
  scale_x_continuous(
    trans = 'log10' 
  ) +
  xlab("Lambda") + ylab("Interval Width") +
  theme_bw() +
  scale_color_discrete(name = expression(abs(beta)))


do.call("rbind", red_res) %>%
  left_join(truth) %>%
  ggplot(aes(x = lambda, y = width, color = truth)) +
  geom_jitter(alpha = .6, width = .05) +
  scale_x_continuous(
    trans = 'log10' 
  ) +
  xlab("Lambda") + ylab("Interval Width") +
  theme_bw() +
  scale_color_discrete(name = expression(abs(beta)))
```

# Profiling

```{r}
set.seed(my_seed)
dat <- gen_data(n = 100, p = 6000, beta = c(-2, -1, -0.5, 0.5, 1, 2, rep(0, 5994)))
tmp <- boot.ncvreg(dat$X, dat$y, time = TRUE)
```

# Beta = 0 + epsilon

## Single Example

```{r}
set.seed(my_seed)
dat <- gen_data(n = 100, p = 60, beta = c(-2, -1, -0.5, 0.5, 1, 2, 0 + 1e-4 * sample(c(-1, 1), 54, replace = TRUE)))
plot(boot.ncvreg(dat$X, dat$y, verbose = FALSE))
```


## Coverage

```{r}
set.seed(my_seed)
res <- boot_sim(beta = c(-2, -1, -0.5, 0.5, 1, 2, 0 + 1e-4 * sample(c(-1, 1), 54, replace = TRUE)))
```

#### Overall Coverage (per bootstrap)

```{r}
mean(res$overall_coverage)
hist(res$overall_coverage, xlab = "Coverage", main ="")
```

#### Individual Coverage (per covariate)

```{r}
tmp <- data.frame(coverage = apply(res$individual_coverage, 2, mean) , beta = res$beta)
plot(abs(tmp$beta), tmp$coverage, xlab = "True Beta Value", ylab = "Coverage")
```


# Beta = 0 + epsilon, large n, larger p

## Single Example

### Plot

```{r}
set.seed(my_seed)
beta0_eps <- 1e-4 * sample(c(-1, 1), 1994, replace = TRUE)
dat <- gen_data(n = 1000, p = 2000, beta = c(-2, -1, -0.5, 0.5, 1, 2, beta0_eps))
tmp <- boot.ncvreg(dat$X, dat$y, verbose = FALSE, time = TRUE)
plot(tmp)
```

### Widths

```{r}
tmp_ci <- ci.boot.ncvreg(tmp)
min(tmp_ci$upper - tmp_ci$lower)
max(tmp_ci$upper - tmp_ci$lower)
```

### Epsilon Coverage

```{r}
mean(c((tmp_ci$upper[-c(1:6)] >= beta0_eps) & (tmp_ci$lower[-c(1:6)] <= beta0_eps)))
```
